---
title: 'Assignment 1: Linear Regression'
output: html_document
---


In Rstudio, you can click the **Knit** button to knit a this Rmarkdown document.

We keep our raw text data, downloaded from Andrew Ng's Coursera course, in plain
`.txt` files. Normally data is saved under the `data` directory in `.Rdata` files,
but since this is the first assignment, we leave the data in text format.

Hence, following Hadley Wickham's recommendations, we place the data in
`inst/extdata`. We can load it with the `read.csv` function, the only trick
is that we need to find the path to the data using `system.file`:

```{r}
library('a1.linear.regression')
path = system.file("extdata", "ex1data1.txt",   package="a1.linear.regression")
data1 = read.csv(path)
```

We can plot the data in R using the basic plotting package:

```{r}
plot(data1$X6.1101, data1$X17.592, xlab = 'Population of city in 10K', ylab = 'Profit in $10K')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
